Group meetings

### 2023-06-05 diapo/groupTemplate/main.tex
Created theme for group meeting template

\documentclass[table]{beamer}
\usetheme{Boadilla}
\usecolortheme{whale}

@@

\title[Group Meeting]
{Weekly group meetings}

@@

\date[26 May] % (optional)
{26 May 2023}

\logo{\includegraphics[height=0.9cm]{figures/logos.png}}

\definecolor{text}{RGB}{25,116,146}
\definecolor{firstRow}{HTML}{219BC3}
\definecolor{evenRow}{HTML}{CCDEE9}
\definecolor{oddRow}{HTML}{E7EFF4}
\definecolor{istblue}{RGB}{0,102,153}
\setbeamercolor{titlelike}{bg=istblue}
\setbeamerfont{title}{series=\bfseries}

@@

  \centering
  \rowcolors{2}{evenRow}{oddRow}
  \begin{tabular}{ c m{3cm} c c c }
    \rowcolor{firstRow}
    & \centering\color{white}Task & \color{white}Done? & \color{white}Why not? & \color{white}Help? \\
    1 & test2 & test23 & test3 & test4\\
    2 & test2 & test23 & test3 & test4\\
    3 & test2 & test23 & test3 & test4\\
    4 & test2 & test23 & test3 & test4\\
    5 & test2 & test23 & test3 & test4\\
  \end{tabular}

@@

  \centering
  \rowcolors{2}{evenRow}{oddRow}
  \begin{tabular}{ c m{4cm} }
    \rowcolor{firstRow}
    & \centering\color{white}Task \cr
    1 & test23 \\
    2 & test23 \\
    3 & test23 \\
    4 & test23 \\
    5 & test23 \\
  \end{tabular}
\end{frame}

@@

  \begin{tikzpicture}
    \node (rect) at (0,0) [rounded corners,draw=text,very thick,minimum width=5.7cm,minimum height=6cm] {Help/collaboration};
    \node (rect) at (6.2,0) [rounded corners,draw=text,very thick,minimum width=5.7cm,minimum height=6cm] {\raggedleft autre chose };
  \end{tikzpicture}
\end{frame}

>>>>

\documentclass[table]{beamer}
\usetheme{gpmeet}
%\usecolortheme{whale}

@@

\title{Group meetings}

@@

\date{26/05/2023}

\logo{
  \begin{tikzpicture}[overlay,remember picture]
    \node[left=0.2cm] at (current page.34){
      \includegraphics[height=1.2cm]{figures/logos}
    };
  \end{tikzpicture}
}

@@

  \centering
  \rowcolors{2}{evenRow}{oddRow}
  \begin{tabular}{ c m{3cm} c c c }
    \rowcolor{firstRow}
    \color{white}\textbf{\#} & \centering\color{white}Task & \color{white}Done? & \color{white}Why not? & \color{white}Help? \\
    1 & test2 & test23 & test3 & test4\\
    2 & test2 & test23 & test3 & test4\\
    3 & test2 & test23 & test3 & test4\\
    4 & test2 & test23 & test3 & test4\\
    5 & test2 & test23 & test3 & test4\\
  \end{tabular}

@@

  \centering
  \rowcolors{2}{evenRow}{oddRow}
  \begin{tabular}{ c m{4cm} }
    \rowcolor{firstRow}
    \color{white}\textbf{\#} & \centering\color{white}Task \cr
    1 & test23 \\
    2 & test23 \\
    3 & test23 \\
    4 & test23 \\
    5 & test23 \\
  \end{tabular}
\end{frame}

@@

  \begin{tikzpicture}
    \node (rect) at (0,0) [rounded corners,draw=text,very thick,minimum width=5.0cm,minimum height=6cm] {Help/collaboration};
    \node (rect) at (6,0) [rounded corners,draw=text,very thick,minimum width=5.0cm,minimum height=6cm] {\raggedleft autre chose };
  \end{tikzpicture}
\end{frame}
